Dynamic Topic Modeling for Voice Dialogues

### 2024-05-03 paper/main.tex
add qmsum
add qwen

\newpage
\textbf{LLM} is a type of artificial intelligence(AI) algorithm that use deep learning techniques and massively large data sets to understand, summarize, generate, and predict new content. 
LLMs are trained with immense amounts of data and use self-supervised learning to predict the next token in a sentence, given the surrounding context. 
Once an LLM has been trained, it can be fine-tuned for a wide range of NLP tasks, including generating and classifying text, answering questions.
The following section will examine the main LLMs used in the article.

@@

@@

\begin{lstlisting}
    <|user|> 
    utterance_1
    utterance_2
    ...
    utterance_n. 
    You have dialogue between two people, 
    extract N topic words. 
    <|assistant|>

@@

\section{Topic extraction}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \hline
        model & TC & TD & TC & TD \\ 
        \hline
        LLaMA3 8B & c & d & c & d \\ 
        Qwen1.5 7B & c & d & c & d \\ 
        Mistral 7B & c & d & c & d \\ 
        \hline
        BertTopic & c & d & c & d \\
        LSA  & c & d & c & d \\
        \hline
    \end{tabular}
\end{center}

>>>>

\newpage
\textbf{LLM} is a type of artificial intelligence(AI) algorithm that use deep learning techniques and massively large data sets to understand, summarize, generate, and predict new content. 
LLMs are trained with immense amounts of data and use self-supervised learning to predict the next token in a sentence, given the surrounding context. 
Once an LLM has been trained, it can be fine-tuned for a wide range of NLP tasks, including generating and classifying text, answering questions.
The following section will examine the main LLMs used in the experiments: LLaMA, Mistral, Qwen.

@@

\subsection{Qwen}

The Qwen LLMs have been extensively trained on up to 3 trillion tokens of diverse text and code examples from a wide range of domains. 
Qwen demonstrate superior performance in various downstream tasks.

In terms of architecture: model based on LLaMA, activation function is SwiGLU, Rotary Embeddings, Pre-Norm and RMSNorm instead LayerNorm.

The pre-training phase involves learning vast amounts of data to gain a comprehensive understanding of the world and its various complexities. 
This includes not only basic language skills, but also advanced skills such as arithmetic, coding and reasoning. 
In this section we introduce the data, model design and scaling, and the extensive evaluation results on benchmark datasets.

The Qwen Series encompasses models that employ SFT and RLHF to align Qwen with human preference. 
Consequently, the Qwen-Chat and its enhanced variant, the Qwen-Chat-RLHF, have been developed. Furthermore, we have created bespoke models for coding and mathematics.

\begin{figure}[h]
    \centering
    \includegraphics[scale=1]{img/qwen.png}
    \caption{Qwen Series}
\end{figure}

For now, there are 5 models of different sizes, 4 of which are opensourced. Specially, Qwen-1.8B, Qwen-7B, Qwen-14B, and Qwen-72B.

@@

\begin{lstlisting}
    <|user|> 
    utterance_1
    utterance_2
    ...
    utterance_n. 
    Extract N key words or pharases 
    that describe the given dialog between two peoples, 
    do not use more than 2 wrods 
    <|assistant|>

@@

\section{Topic extraction}

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \hline
        model & TC & TD & TC & TD \\ 
        \hline
        LLaMA3 8B & c & d & c & d \\ 
        Qwen1.5 7B & c & d & c & d \\ 
        Mistral 7B & c & d & c & d \\ 
        \hline
        BertTopic & c & d & c & d \\
        LSA  & c & d & c & d \\
        \hline
    \end{tabular}
\end{center}
